Footpath Planning for Example-driven Procedural Road Networks

### 2020-03-17 paper/paper.tex
Change description of S_T value range
Fix report do that it compiles

The turning function was first defined by Arkin et al. (1991), as a method for measuring the similarity of two polygons. The Turning funciton $T_c(l)$ measures the cumulative angle of the polygon's counter-clockwise tangent, as a function of the cumulative normalized length l. This project uses the turning function as it is defined by (Fan et al., 2014). For a polygon with vertices ${v_1 ... v_n}$ and line segments ${e_1 ... e_n}$ It is defined as follows.
Fix a starting vertex $v_1$.
The tangent angle at $v_1$ is $\theta_{n,1}$. This is the angle between the neighbouring line segments $e_n$ and $e_1$.
For any $i$ such that $i>1$ and $n<i$, the tangent angle at $v_i$ is recursively defined as: $\theta_{i, i-1} = \theta_{n,1} + \sum^{i}_{k=1} \theta_{k, k-1}$
The turning function has some nice geometric properties, in that it is invariant to both rotation and scaling of the polygon. The function contains no information of the orientation of the polygon, only of the relative angle between successive line segments, thus it does not change under roation. It also measures only the normalized cumulative length, which does not change under scaling.
The similarity of two polygons A and B in terms of their turning function is defined as their distance of their cumulative turning functions: $S_{T}(A, B) = 1 - (\int^{1}_{0} T_{C,A}(l) - T_{C,B}(l) dl)^{1/2}$.
The value range of $S(A, B)$ will be 0 to 1, where $S(A,B) = 1$ if the polygons are identical.

@@

The relative overlap may also be used to determine building matching relations even when the semantic accuracy is low. If a large building is represented by a single footprint in one dataset but by several smaller footprints in the other, XXX found that if $S_{RO}(foot_{A}, foot_{B}) < 30\%$ for two buildings $A$ and $B$ from different sets, then $A$ and $B$ are highly likely to be separate, neighbouring buildings and not in fact identical. Therefore we will here assume that two buildings are matching candidates if their relative area overlap is greater than 30\%. If a one-to-many object matching is found, the compound perimeter of the footprints in the many-set will be used when calculating the turning function and finding closest vertices between the polygons.

@@

\bitiem{fan-14}
(Fan et al, 2014), Quality assessment for building footprints data on OpenStreetMap \\
\href{https://www.researchgate.net/publication/262163378\_Quality\_assessment\_for\_building\_footprints\_data\_on\_OpenStreetMap}.

>>>>

The turning function was first defined by Arkin et al. (1991), as a method for measuring the similarity of two polygons. The Turning function $T_c(l)$ measures the cumulative angle of the polygon's counter-clockwise tangent, as a function of the cumulative normalized length l. This project uses the turning function as it is defined by (Fan et al., 2014). For a polygon with vertices ${v_1 ... v_n}$ and line segments ${e_1 ... e_n}$ It is defined as follows.
Fix a starting vertex $v_1$.
The tangent angle at $v_1$ is $\theta_{n,1}$. This is the angle between the neighbouring line segments $e_n$ and $e_1$.
For any $i$ such that $i>1$ and $n<i$, the tangent angle at $v_i$ is recursively defined as: $\theta_{i, i-1} = \theta_{n,1} + \sum^{i}_{k=1} \theta_{k, k-1}$
The turning function has some nice geometric properties, in that it is invariant to both rotation and scaling of the polygon. The function contains no information of the orientation of the polygon, only of the relative angle between successive line segments, thus it does not change under roation. It also measures only the normalized cumulative length, which does not change under scaling.
The similarity of two polygons A and B in terms of their turning function is defined as their distance of their cumulative turning functions: $S_{T}(A, B) = 1 - (\int^{1}_{0} T_{C,A}(l) - T_{C,B}(l) dl)^{1/2}$.
The value range will be $(0 < S_{T} < 1)$, where $S_{T}(A,B) = 1$ if the polygons are identical.

@@

The relative overlap may be used to determine building matching relations even when the semantic accuracy is low. If a large building is represented by a single footprint in one dataset but by several smaller footprints in the other, XXX found that if $S_{RO}(foot_{A}, foot_{B}) < 30\%$ for two buildings $A$ and $B$ from different sets, then $A$ and $B$ are highly likely to be separate, neighbouring buildings and not in fact identical. Therefore we will here assume that two buildings are matching candidates if their relative area overlap is greater than 30\%. If a one-to-many object matching is found, the compound perimeter of the footprints in the many-set will be used when calculating the turning function and finding closest vertices between the polygons.

@@

\bibitem{fan-14}
(Fan et al, 2014), Quality assessment for building footprints data on OpenStreetMap \\
\href{https://www.researchgate.net/publication/262163378\_Quality\_assessment\_for\_building\_footprints\_data\_on\_OpenStreetMap}.
